---
title: "Lab 2.3"
author: "Yan Guanyu"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Basic Commands

```{r}
x <- c(1, 3, 2, 5)
x

x = c(1, 6, 2)
y = c(1, 4, 3)
x

length(x)
length(y)
x + y 
```

ls() function is used to check a list of all of the saved objects, such as data and functions.

rm() function is used to remove objects

```{r}
ls()

rm(x,y)
ls()
```

Remove all objects at once:

```{r}
rm(list = ls())
```

matrix function can be used to create matrix

```{r}
x <- matrix(data = c(1, 2, 3, 4), nrow = 2, ncol = 2)
x

x <- matrix(c(1,2,3,4), 2, 2)
x

matrix(c(1, 2, 3, 4), 2, 2, byrow = TRUE)

sqrt(x)
```

rnorm(n, mean, sd) function generates a vector of random normal variables, n: sample size

```{r}
x <- rnorm(50)
y <- x + rnorm(50, mean = 50, sd = .1)
cor(x, y)

set.seed(1303)
rnorm(50)

set.seed(3)
y <- rnorm(100)
mean(y)
var(y)
sqrt(var(y))
sd(y)
```

## Graphics

Scatter plot: plot(x, y)

```{r}
x <- rnorm(100)
y <- rnorm(100)
plot(x, y)
plot(x, y, xlab = "this is the x-axis", ylab = "this is the y-axis", main = "Plot of X vs Y")

pdf("Figure.pdf")
plot(x, y, col = "green")
dev.off()
```

seq() function can be used to create a sequence of numbers

```{r}
x <- seq(1, 10)
x
x <- 1:10
x
x <- seq(-pi, pi, length= 50)
x
```

contour plot: represent 3-d data using contour(x, y, z)

heat plot: image()

persp() : 3-d plot

```{r}
y <- x
f <- outer(x, y, function(x,y) cos(y) / (1 + x^2))
contour(x, y, f)
contour(x, y, f, nlevels  = 45, add = T)

fa <- (f - t(f)) / 2
contour(x, y, fa, nlevels = 15)

image(x, y, fa)
persp(x, y, fa)
persp(x, y, fa, theta = 30)
persp(x, y, fa, theta = 30, phi = 20)
persp(x, y, fa, theta = 30, phi = 70)
persp(x, y, fa, theta = 30, phi = 40)
```

## Indexing Data

```{r}
A <- matrix(1:16, 4, 4)
A
```

```{r}
A[2, 3] 
```

```{r}
A[c(1, 3), c(2, 4)]
```

```{r}
A[1:3, 2:4]
```

```{r}
A[1:2, ]
```

```{r}
A[, 1:2]
```

```{r}
A[1, ]
```

```{r}
A[-c(1, 3), ]
A[-c(1, 3), -c(1,3,4)]
```

```{r}
dim(A)
```

## Loading Data

```{r}
Auto <- read.table("Auto.data")
View(Auto)
head(Auto)
```

```{r}
Auto <- read.table("Auto.data", header = T, na.string = "?", stringsAsFactors = T)
View(Auto)
```

na.string: any time it sees a particular character or set of characters, it should be treated as a missing element of the data matrix.

stringAsFactors = T means any variable containing character strings should be interpreted as a qualitative variable, and that each distinct character string represents a distinct level for that qualitative variable.

```{r}
Auto <- read.csv("Auto.csv", na.strings = "?", stringsAsFactors = T)
View(Auto)
dim(Auto)
Auto[1:4, ]
```

remove rows contain na:

```{r}
Auto <- na.omit(Auto)
dim(Auto)
names(Auto)
```

## Additional Graphical and Numerical Summaries

```{r}
plot(Auto$cylinders, Auto$mpg)
attach(Auto)
plot(cylinders, mpg)
```

as.factor() converts quantitative variables into qualitative variables.

```{r}
cylinders <- as.factor
```

```{r}
plot(cylinders, mpg)
plot(cylinders, mpg, col = "red", varwidth = T)
plot(cylinders, mpg, col = "red", varwidth = T, horizontal = T)
plot(cylinders, mpg, col = "red", varwidth = T, horizontal = T, xlab = "cylinders", ylab = "MPG")
```

histogram: hist()

```{r}
hist(mpg)
hist(mpg, col = 2)
hist(mpg, col = 2, breaks = 15)
```

pairs(): scatterplot matrix

```{r}
pairs(Auto)
pairs(
  ~ mpg + displacement + horsepower + weight + acceleration,
  data = Auto
)
```

identify(): identify the value of a particular

```{r}
plot(horsepower, mpg)
identify(horsepower, mpg, name)
```

summary(): numerical summary of each variable in a particular data set

```{r}
summary(Auto)
```

```{r}
summary(mpg)
```
