---
title: "Lab 3_6"
author: "Yan Guanyu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries

library() function is used to load libraries, or groups of functions and datasets that are not included in the base R distribution

```{r}
library(MASS)
library(ISLR2)
```

# Simple Linear Regression

ISLR2 library contains the Boston data set. We will seek to predict medv using 12 predictors such as rm, and lstat.

```{r}
head(Boston)
```

Using lm(fucntion) to fit a simple linear regression model, with medv as the response and lstat as the predictor

```{r}
lm.fit <- lm(medv ~ lstat, data = Boston)
attach(Boston)
lm.fit
summary(lm.fit)
```

We could use names() function in order to find out what other pieces of information are stored in lm.fit.

```{r}
names(lm.fit)
coef(lm.fit)
```

In order to obtain a confidence interval for the coefficient estimates, we can use the confint() command.

```{r}
confint(lm.fit)
```

predict() : prediction intervals

```{r}
predict(lm.fit, data.frame(lstat = (c(5, 10, 15))), interval = "confidence")
predict(lm.fit, data.frame(lstat = (c(5, 10, 15))), interval = "prediction")
```

plot medv and lstat along with the least squares regression line using plot() and abline()

```{r}
plot(lstat, medv)
abline(lm.fit, lwd = 3, col = "red")
plot(lstat, medv, col = "red")
plot(lstat, medv, pch = 20)
plot(lstat, medv, pch = "+")
plot(1:20, 1:20, pch = 1:20)


```

```{r}
par(mfrow = c(2, 2))
plot(lm.fit)
plot(predict(lm.fit), residuals(lm.fit))
plot(predict(lm.fit), rstudent(lm.fit))
plot(hatvalues(lm.fit))  ## Leverage statistics
which.max(hatvalues(lm.fit)) 
```

# Multiple Linear Regression

```{r}
lm.fit <- lm(medv ~ lstat + age, data = Boston)
summary(lm.fit)
```
